An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/impl.tex
maybe i didnt send everything?

The \lstinline{check} function will start will all the rules we have learned, and filter until we only have the rules that have been broken by the file of interest.
We first eliminate the rules that pass the probability check defined in ($\S$\ref{subsec-rules}).
Second, we only consider the rules which are relevant to the file - we do not need to check rules about keywords which do not appear in the file.
Lastly, we take the errors as any rule that does not hold over the given file.

@@

Since we learn a set of rules on each file in isolation from the other, we have a pleasingly parallel situation.
Haskell allows us to easily take advantage of this by using the parallel
mapping library \cite{parallel}, both for translation to the intermediate representation, and for learning the rules on each file.
The merge stage could also easily be parallelized, using a divide and conquer approach, but \app runs fast enough over our learning set (28 files, 961 lines of code) that this has not been necessary.

>>>>

The \lstinline{check} function will start will all the rules we have learned, and filter until we only have the rules that have been broken by the file of interest.
We first eliminate the rules that do not pass the probability check defined in ($\S$\ref{subsec-rules}).
Second, we only consider the rules which are relevant to the file - we do not need to check rules about keywords which do not appear in the file.
Lastly, we take the errors as any rule that does not hold over the given file.

@@

Since we learn a set of rules on each file in isolation from the other, we have a pleasingly parallel situation.
Haskell allows us to easily take advantage of this by using the parallel mapping library \cite{parallel}, both for translation to the intermediate representation, and for learning the rules on each file.
The merge stage could also be parallelized, using a divide and conquer approach, but this is not a priority since the learning stage only needs to be run once per learning set, and can then be cached (in our case, as a .json file) for fast reading when doing verification.
